---
title: "M-you-sic"
<<<<<<< HEAD
author: "Olivia Sapp, Terra Shrestha, Jermey He, Harry Hall"
date: "11/14/2022"
=======
author: "Olivia Sapp, Terra Shresths, Jeremy He, Harry Hall"
date: "11/22/2022"
>>>>>>> 389abf6a660c28e2d79a60cfc099e5e70d5b4b2e
output: html_document
---


```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../source/summary.R")
```

### Dynamic Paragraph
The values that were calculated from the data includes, name, country, date, position, streams, artists, genres. Each of these values are grouped by the top 100 streams in 2022. Also, all songs are grouped globally, instead of by country. When finding summary information, we looked at the max of each value. The first value, name, represents the title of each song. In the Top 100 data set that was used, “Pepas” was the song name that contained the most streams. 999975 streams were collected from the song “Pepas”.  The date when these amount streams were recorded was 2022-09-22. At this date, the position (which is the ranking) of this song was 158. By using the summary function again, the artist with the most number of streams was Farruku – the singer of “Pepas”. Lastly, the genre of this was Latin hip hop, trap Latino, and reggaeton. 


### Table of Aggregated Data
```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
spotiify_origional <- read.csv("https://raw.githubusercontent.com/info201a-au2022/project-group-1-section-aa/main/data/charts.csv")

spotify_modify <- spotiify_origional %>% 
  select(name, country, date, position, streams, artists, genres = artist_genres)

spotify_2022_global <- spotify_modify %>% 
  filter(date >= "2022-01-01") %>% 
  filter(country == "global") %>% 
  arrange(date) %>% 
  group_by(date)

# Most popular 100 songs in the globe
top_100 <- spotify_2022_global[order(spotify_2022_global$streams, decreasing = TRUE), ]
top_100 <- top_100[1:100, ]

top_100 

```
Our table looks at the global Spotify data from 2022. It has the top 100 songs from this year based on streams. The tale is grouped by streams. From this table we can observe that popular genres include  pop, dance pop, k-pop, rock, and latin rap/trap. All of these songs had 988530 or more streams in one day.  


### Chart 1: Bar Chart
```{r, echo=FALSE}
spotiify_origional <- read.csv("https://raw.githubusercontent.com/info201a-au2022/project-group-1-section-aa/main/data/charts.csv")
View(spotiify_origional)
# filters down the data
# removes the track id, explicit, and duration columns
spotify_modify <- spotiify_origional %>% 
  select(name, country, date, position, streams, artists, genres = artist_genres)

#returns all the data just from 2022
#this is the data set you should you on the project
spotify_2022 <- spotify_modify %>% 
  filter(date >= "2022-01-01") %>% 
  arrange(date) %>% 
  group_by(date)

# use write.csv() to turn the new dataset into a .csv file
#write.csv(Your DataFrame,"Path to export the DataFrame\\File Name.csv", row.names = FALSE)
#write.csv(spotify_2022, "/Users/oliviasapp/Documents/info201/project-group-1-section-aa/data/spotify_2022.csv" , row.names = FALSE)

# then I pushed the spotify_2022.csv to the GitHub repo
View(spotiify_origional)

spotify_2022_global <- spotify_modify %>% 
  filter(date >= "2022-01-01") %>% 
  filter(country == "global") %>% 
  arrange(date) %>% 
  group_by(streams)
View(spotify_2022_global) 

top_3 <- spotify_2022_global[order(spotify_2022_global$streams, decreasing = TRUE), ]
top_3 <- top_3[1:3,]
top_3$streams <- as.numeric(top_3$streams)
View(top_3)  

col_chart <- ggplot(data = top_3) + 
  geom_col(mapping = aes(x = name, y = streams)) +
  ggtitle("Top Three Songs Daily Streamed Globally") +
  theme(plot.title = element_text(hjust = 0.5))
col_chart <- col_chart + coord_cartesian(ylim = c(999000,1000000))
col_chart

```

The bar chart we have created compares the three most popular songs and how many streams they have on a daily basis. The most interesting thing about the bar chart is that two of the three songs have the same genre “pop”, and the other falls in the “latin hip hop” genre. The genres may have correlation to the popularity of songs in the top 100 we feel from this first data visualization. Over the next two charts we will explore more about favorite genres across the globe and not just the relationship between the top 3.

### Chart 2: Mapping
```{r, echo=FALSE}
source("../source/mapping_chart.R")
plot(map_chart)
```
This map looks at the most popular song of 2022,Pepas by Farruko, across the globe. If this song was streamed a lot by the people of one country then their country will be yellow. If not, then the country will be blue. And if there is no data on that country it will be gray. It seems like Pepas was a popular song in Latin America and Europe this year. These countries have enough streaming influence over the spotify charts that they were able to make it the top song.

### Chart 3: Pie Chart
```{r, echo=FALSE}
source("../source/pie_chart.R")
plot(pie)
```

This chart summarizes the top 10 most favorable genres across the globe. The purpose of this is to ascertain which genre is most popular. Therefore that genre can eventually be used to bridge the gap between people from different cultures in terms of musical ideas and thoughts. For example, according to the data, pop is the most popular music genre. So when in conversations, people can start off the topic by pointing out who your favorite pop star is or what their favorite pop music is. This result can also be used for later studies to explore why “pop” has become the star of music.


